Quiz 3
========================================================

Question 1
----------------------------
Take a look at the 'iris' dataset that comes with R. 
The data can be loaded with the code:

```{r}
library(datasets)
data(iris)

```

There will be an object called 'iris' in your workspace. In this dataset, what is the mean of 'Sepal.Length' for the species virginica?

```{r}
tapply(iris$Sepal.Length,iris$Species,mean)

# or this way
tapply(iris$Sepal.Length,iris$Species%in%c("virginica"),mean)

# or this way
tapply(iris$Sepal.Length,iris$Species=="virginica",mean)
```


Question 2
-----------------------------------
Continuing with the 'iris' dataset from the previous Question, what R code returns a vector of the means of the variables 'Sepal.Length', 'Sepal.Width', 'Petal.Length', and 'Petal.Width'?
```{r}
apply(iris, 2, mean)
rowMeans(iris[, 1:4])
apply(iris[, 1:4], 2, mean)
apply(iris[, 1:4], 1, mean)
```


Question 3
----------------------------------
Load the 'mtcars' dataset in R with the following code
```{r}
library(datasets)
data(mtcars)
```

How can one calculate the average miles per gallon (mpg) by number of cylinders in the car (cyl)?
```{r}
tapply(mtcars$cyl, mtcars$mpg, mean)
split(mtcars, mtcars$cyl)
sapply(split(mtcars$mpg, mtcars$cyl), mean)
mean(mtcars$mpg, mtcars$cyl)
```

Question 4
---------------------
Continuing with the 'mtcars' dataset from the previous Question, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?


```{r}
tapply(mtcars$hp, mtcars$cyl, mean)
lapply(split(mtcars$hp, mtcars$cyl), mean)$'8' - lapply(split(mtcars$hp, mtcars$cyl), mean)$'4'
```

