Quiz 2
========================================================

Quesion 1
----------------------
Suppose I define the following function in R:
```{r q1 function}
cube <- function(x, n) {
        x^3
}

```

What is the result of running:
```{r cube}
cube(3)
```


Question 2
--------------------------
The following code will produce a warning in R.

```{r q2 function}
x <- 1:10
if(x > 5) {
        x <- 0
}
```
Why? 

Question 3
---------------------------
Consider the following function

```{r q3 function}
ff <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
# changed f to ff so it wouldn't confuse the code later on!
```

then run:
```{r run}
z <- 10
f(3)
```
What value is returned?

Question 4
-------------------------
Consider the following expression:

```{r q4 function}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```

What is the value of 'y' after evaluating this expression?
```{r y}
y
```

Question 5
---------------------------------
Consider the following R function
```{r q5 function}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```

Which symbol in the above function is a free variable?
 
 * see notes on free variables [here](http://www.stat.berkeley.edu/~statcur/Workshop2/Presentations/functions.pdf)
 * The scoping rules determine how a value is associated with a free variable in a function
 * The scoping rules of a language determine how values are assigned to free variables. 
 * Free variables are not formal arguments and are not local variables (assigned insided the function body).
 * __options are: f,z,d,L,g__

```{r free variable}
x <- 1:10
h(x)
```

### Questions 6-10

__answers are all found [here](http://www.stat.berkeley.edu/~statcur/Workshop2/Presentations/functions.pdf)__